Forecasting Influenza Hospitalizations Using a Bayesian Hierarchical Nonlinear Model with Discrepancy

### 2024-12-03 manuscript/manuscript.tex
fix arxiv tex

% \section{Abstract}
\begin{abstract}
The annual influenza outbreak leads to significant public health and economic burdens making it desirable to have prompt and accurate probabilistic forecasts of the disease spread. The United States Centers for Disease Control and Prevention (CDC) hosts annually a national flu forecasting competition which has led to the development of a variety of flu forecast modeling methods. For the first several years of the competition, the target to be forecast was weekly percentage of patients with an influenza-like illness (ILI), but in 2021 the target was changed to weekly hospitalization counts. Reliable state and national hospitalization data has only been available since 2021, but for ILI the data has been available since 2010 and has been successfully forecast for several seasons. % Modeling hospitalization data alone is limited to the relatively small amount of data, 
% but may be supplemented by existing ILI data which has been reported, 
% published at the state level, and successfully forecast for over a decade. 
In this manuscript, we introduce a two component modeling framework for forecasting weekly hospitalizations utilizing both hospitalization data and ILI data. The first component is for modeling ILI data using a dynamic nonlinear Bayesian hierarchical model. The second component is for modeling hospitalizations as a function of ILI. For hospitalization forecasts, ILI is first forecasted and then hospitalizations are forecast with ILI forecasts used as a linear or quadratic predictor. In a simulation study, two ILI forecast models, including one similar to the winning model for two seasons of the CDC forecast competition from \cite{osthus2019dynamic} and a nonlinear Bayesian hierarchical model from \cite{ulloa2019} are compared. Also assessed is the usefulness of including a systematic model discrepancy term in the ILI model. Forecasts of state and national hospitalizations for the 2023-24 flu season are made, and different modeling decisions are compared. We found that including a discrepancy component in the ILI model tends to improve forecasts during certain weeks of the year. We also found that other modeling decisions such as the exact nonlinear function to use in the ILI model or the error distribution for hospitalization models may or may not be better than other decisions, depending on the season, location, or week of the forecast.
% We compare hospitalization forecasts from our model to other related models submitted to the CDC forecasting competition.

@@

\begin{figure}
    \centering
    \includegraphics[scale=.7]{Images/us_ili_seasons.png}
    \caption{Percentage of outpatient visits with an influenza-like illness (ILI) in the US for seasons 2010 to 2023. Week 1 is the first week of August of the year the flu season begins and the last week of the season is the last week of July of the following year.}
    \label{fig:us_ili}
\end{figure}

@@

 \begin{figure}
    \centering
    \includegraphics[scale=.7]{Images/ili_vs_week.png}
    \caption{Percentage of outpatient visits with an influenza-like illness (ILI) in five different states and the District of Columbia for seasons 2010 to 2023. Week 1 is the first week of August of the year the flu season begins and the last week of the season is the last week of July of the following year.
     Plots include lines for ILI\% from the 2010 flu season to 2023 (grey) and for the weekly ILI averaged over all seasons (black).}
    \label{fig:ili_vs_week}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.5]{Images/us_hospitalizations.png}
    \caption{Weekly flu confirmed hospitalization counts at the national level for 2022 (left) and 2023 (right) flu seasons}
    \label{fig:us_hosp}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.65]{Images/hosp_vs_week.png}
    \caption{Weekly hospitalization counts for five states and DC for the 2022 (grey) and 2023 (black) flu seasons}
    \label{fig:hosp_vs_week}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.6]{Images/ili_vs_hosp.png}
    \caption{Weekly flu confirmed hospitalization counts ($y$-axis) for five states and the District of Columbia for the 2022 and 2023 flu seasons plotted against ILI\% ($x$-axis)}
    \label{fig:ili_vs_hosp}
\end{figure}

@@

% \begin{figure}
%     \centering
%     \includegraphics[scale=.8]{Images/hosp_preds_ili_22.png}
%     \caption{Weekly hospitalization counts during the 2022 flu season for 5 states and DC (black dots) and predicted weekly hospitalizations from the fit of model (\ref{eq:simple_hosp_reg}) (red lines)}
%     \label{fig:hosp_preds_ili_22}
% \end{figure}
% \jarad{Make the relationship between the data in the previous plot and this plot clear.}

@@

The proposed model for ILI for any location is given in (\ref{eq:ili_model}). Here $ILI_{s,w}$ is the ILI for flu season $s$ and week $w = 1, 2, ..., W$, where $W = 52$ or $W = 53$, depending on how many Sundays there are in a given season. The ILI is a proportion, so the Beta random variable is a natural selection for modeling. Under the parameterization in of the Beta distribution used in (\ref{eq:ili_model}) the expected value is $\pi_{s,w}$ and the variance is $\pi_{s,w}(1 - \pi_{s,w})/(1 + \kappa_s)$, making $\kappa_s$ a scale parameter. The nonlinear function $f_{\theta_s}(w)$ captures the trajectory of the ILI, and $\gamma_w$ is a discrepancy term for capturing the systematic patterns which $f_{\theta_s}(w)$ does not capture.

\begin{equation}
    \label{eq:ili_model}
    \begin{flalign*}
        &ILI_{s,w} \overset{ind}{\sim} \text{Beta}(\pi_{s,w}\kappa_s,\; \kappa_s(1 - \pi_{s,w})) \\
        &\text{logit}(\pi_{s,w}) = f_{\theta_s}(w) + \gamma_w
    \end{flalign*}
\end{equation}
In \cite{osthus2019dynamic} $f_{\theta_s}(w) = \text{logit}(I_{s,w})$ where $I_{s,w}$ is the infectious compartment of the SIR model from (\ref{eq:sir_diff}) in section \ref{sec:sir_func}. In \cite{ulloa2019} $f_{\theta_s}(w) = ASG_{\theta}(w)$ from (\ref{eq:asg_function}) in section \ref{sec:asg_func}. In \cite{ulloa2019} modeling is done hierarchically over seasons. 
% The SIR and ASG functions are defined in the next two subsections.
% and $\gamma_w$ is modeled as a reverse random walk as in (\ref{eq:rw}).

@@

\begin{figure}
    \centering
    \includegraphics[scale=.6]{Images/sir_traj.png}
    \caption{Susceptible-infectious-recovered (SIR) model separated by compartments. The three compartments are the susceptible compartment (left), infectious (center), and recovered (right). In this example, $S_0/\rho > 1$.}
    \label{fig:sir_traj}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.45]{Images/asg_function.png}
    \caption{Example plot of asymmetric Gaussian (ASG) function showing the shape of the function in relation to the parameters $\lambda, \; \eta, \; \mu, \; \sigma_1, \; \text{and} \; \sigma_2$}
    \label{fig:asg_function}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.5]{Images/asg_fits.png}
    \caption{Observed US national influenza-like illness (ILI) percentage for seasons 2010 to 2022 excluding 2020 (grey) overlaid with MLE of an asymmetric Gaussian (ASG) model for the ILI data (black)}
    \label{fig:asg_fits}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.45]{Images/discrepancy.png}
    \caption{Difference between observed US national influenza-like illness (ILI) and MLE fits for an asymmetric Gaussian (ASG) model for each season 2010 to 2022 excluding 2020 (grey) and the average difference of all seasons (black)}
    \label{fig:discrepancy}
\end{figure}

The term $\gamma_w$, where $w$ is the season week, is included in (\ref{eq:ili_model}) to capture the per week discrepancy between ILI and the function. Modeling discrepancy has been used in uncertainty analysis of simulators to capture systematic differences between mathematical models and 
reality \cite[]{ma2022multifidelity,brynjarsdottir2014learning,arendt2012improving,kennedy2001bayesian}. Modeling discrepancy can lead to overfitting, particularly in forecasting scenarios, and may also lead to identifiability issues. 
Thus, care must be taken in setting parameter constraints as well as in the selection of prior distributions \cite[]{osthus2019dynamic,brynjarsdottir2014learning}. 
Modeling of the discrepancy for ILI was done by \cite{osthus2019dynamic} during the 2015 and 2016 flu seasons where their model outperformed all others in the CDC flu forecasting challenge \cite[]{osthus2019dynamic}. As in Osthus's model, $\gamma_w$ is modeled as a reverse random walk, as shown in (\ref{eq:rw}). 
\begin{equation}
    \label{eq:rw}
        \gamma_w|\gamma_{w + 1} &\overset{ind}{\sim} N(\gamma_{t+1},\sigma^2_{\gamma}), \quad
        \gamma_{W} &\sim N(0,\sigma^2_{\gamma_W})
\end{equation}
The idea for using the reverse random walk is that there are several previous seasons of ILI data, and assuming the random walk captures systematic behavior, fitting it hierarchically over seasons can assist in predicting future behavior in the current season. 
Reverse random walks have also been used with success in election forecasting and other flu forecasting models \cite[]{osthus2021multiscale, osthus2019dynamic, linzer2013dynamic}. The sum to zero constraint $-\gamma_1 = \sum_{w=2}^W \gamma_w$ is imposed on (\ref{eq:rw}) to improve identifiability.

@@

% \begin{equation}
%     \label{eq:shared_priors}
%     \begin{align*}
%         \kappa_s &\overset{ind}{\sim} N^+(0, 10,000^2) \\
%         \sigma_{\gamma}^2 &\sim N^+(0, .02^2) \\
%         \sigma_{\gamma_W}^2 &\sim N^+(\hat{\sigma}_W^2, 1^2) \\
%         \alpha_{0s} &\overset{ind}{\sim} N(0, 5^2) \\
%         \alpha_{1s} &\overset{ind}{\sim} N(0, 5^2) \\
%         \alpha_{2s} &\overset{ind}{\sim} N(0, 5^2) \\
%         \phi &\sim N(0, .4)\mathbbm{1}_{(-1,1)} \\
%         \sigma_{\epsilon_s} &\overset{ind}{\sim} N^+(0, 4^2) \\
%         \omega_s &\overset{ind}{\sim} N^+(0, 15^2)
%     \end{align*}
% \end{equation}
% \jarad{Generally introduce the distribution families in the methods, but the distributions themselves when performing the data analysis. Here I think you just need to say that you are using normals for unrestricted parameters, positive normals for positive parameters and a normal truncated on (-1,1) for the correlation. Also mention they are all independent (which I guess was done before.}

@@

The models were fit via Markov chain Monte Carlo (MCMC) sampling using the \texttt{cmdstanr} package which was developed and is maintained by the \cite{stan2024manual} \cite[]{gabry2022stan}. Stan implements Hamiltonian Monte Carlo (HMC) sampling with the No-U-turn sampler \cite[]{hoffman2014no}. The \texttt{cmdstanr} package provides several diagnostic statistics for assessing the sampler.
As mentioned, most model parameter prior distributions were intended to be uninformative. Appendix \ref{app:B_prior} shows plots of posterior distributions for select parameters from ILI and hospitalization models.

@@

\begin{table}
\caption{Maximum $\hat{R}$ and minimum $ESS$ over all parameters for six hospitalization models fitted on US data for week 14 of the 2023 season}
\label{tab:hsop_diagnostics}
\begin{center}
    \begin{tabular}{c|cccccc}
     & NORM & NORM^2 & LNORM & LNORM^2 &  LST &  LST^2 \\
     \hline
     $\hat{R}$ & $< 1.001$ & $< 1.001$ & $< 1.001$ & $< 1.001$ & $< 1.001$ & $< 1.001$\\
     $ESS$  & 71,266 & 73,554 & 46,747 & 54,975 & 7,660 & 62,663 \\
    \end{tabular}
    \end{center}
\end{table}

@@

\begin{equation}
    \text{CRPS}(F, y^*) = \int_{-\infty}^{\infty} (F(x) - \mathbbm{1} (y^* \leq x))^2 dx
    \label{eq:crps2}
\end{equation}

@@

\begin{figure}
\centering
% \begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[scale=.35]{Images/overall_crps.png}
    % \caption{Boxplots of CRPS for the four ILI models over all seasons, weeks, and horizons in the simulation study}
% \end{subfigure}%
% \begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[scale=.35]{Images/overall_logs.png}
    % \caption{Boxplots of LogS for the four ILI models over all seasons, weeks, and horizons in the simulation study}}
% \end{subfigure}
\caption{Boxplots of the continuous ranked probability score (CRPS) (left) and logarithmic score (LogS) (right) for the four ILI models over all seasons, weeks, and horizons in the simulation study}
\label{fig:overall_scores}
\end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[scale=.6]{Images/overall_crps.png}
%     \caption{Boxplots of CRPS for the four ILI models over all seasons, weeks, and horizons in the simulation study}
%     \label{fig:crps_overall}
% \end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.5]{Images/crps_by_season.png}
    \caption{Boxplots of continuous ranked probability score (CRPS) for the four ILI models over all weeks and horizons in the simulation study faceted by season and including seasons 2010-2022, excluding 2020}
    \label{fig:crps_by_season}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.5]{Images/crps_by_week_horizon.png}
    \caption{Boxplots of continuous ranked probability score (CRPS) for the four ILI models over all seasons in the simulation study faceted by horizon (x-axis) and week (y-axis). Horizons include 1-4 week ahead forecastss and weeks include weeks 14, 20, 26, 32, and 38 of the flu season}
    \label{fig:crps_by_week_horizon}
\end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[scale=.6]{Images/overall_logs.png}
%     \caption{Boxplots of LogS for the four ILI models over all seasons, weeks, and horizons in the simulation study}}
%     \label{fig:logs_overall}
% \end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.5]{Images/logs_by_season.png}
    \caption{Boxplots of logarithmic score (LogS) for the four ILI models over all weeks and horizons in the simulation study faceted by season and including seasons 2010-2022, excluding 2020.}
    \label{fig:logs_by_season}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.5]{Images/logs_by_week_horizon.png}
    \caption{Boxplots of logarithmic (LogS) for the four ILI models over all seasons in the simulation study faceted by horizon (x-axis) and week (y-axis). Horizons include 1-4 week ahead forecasts and weeks include weeks 14, 20, 26, 32, and 38 of the flu season.}
    \label{fig:logs_by_week_horizon}
\end{figure}

@@

In this section we apply the forecast models to make forecasts of the 2023 flu season weekly hospitalizations. The scoring of the forecasts is in the context of the FluSight competition where each competing forecast was submitted as a set of 23 quantiles corresponding to the given probability levels $(0.010, 0.025, 0.050, 0.100, 0.150, …, 0.950, 0.975, 0.990)$. A single forecast is thus comprised of 11 predictive intervals and a median.
Forecasts of 1, 2, 3, and 4-week ahead hospitalization counts were requested, and forecasts were made at the state and national level. The first week of forecasting took place during the week of October 7, 2023, and the final week was the week of April 27, 2024 making 29 total weeks of forecasts.
 The same format was used during the 2021 and 2022 seasons and for the COVID-19 Forecast Hub \cite[]{mathis2024evaluation, bracher2021evaluating}. 
% Nearly teams participated and forecasts from over 40 models were submitted throughout the duration of the season. 
 Primary scores for evaluating each forecast were the weighted interval score (WIS), the log-weighted interval score (LWIS), and the relative weighted interval score (RWIS). The focus in this section will be on the LWIS (see appendix \ref{app:A_rwis} for RWIS based results).

@@

\begin{equation}
\label{eq:is}
        IS_{\alpha}(l,r;y^*) = (r-l) + \frac{2}{\alpha}(l - y^*)\mathbbm{1}\{y^* < l\} + \frac{2}{\alpha}(y^* - r) \mathbbm{1}\{y^* > r\}
\end{equation}

We fit 24 forecast models for each location for all 29 weeks, and for each week forecast 1-4 week ahead hospitalizations. The 24 models included all combinations of ASG, ASGD, SIR, and SIRD ILI models, the NORM, LNORM, and LST hospitalization models, and both quadratic and linear hospitalization models. 
The prior distributions under the SIR model are in (\ref{eq:sir_prior}). Because we set $S_{0s} = 0.9$, prior distributions were assigned only to $I_{0s}$, $\beta_s$ and $\rho_s$, recalling the parameter for the recovery rate $\delta_s = \rho_s \beta_s$. Here $\mathbbm{1}_{A}$ represents the indicator function for values within the set $A$.

>>>>

\begin{abstract}
The annual influenza outbreak leads to significant public health and economic burdens making it desirable to have prompt and accurate probabilistic forecasts of the disease spread. The United States Centers for Disease Control and Prevention (CDC) hosts annually a national flu forecasting competition which has led to the development of a variety of flu forecast modeling methods. For the first several years of the competition, the target to be forecast was weekly percentage of patients with an influenza-like illness (ILI), but in 2021 the target was changed to weekly hospitalization counts. Reliable state and national hospitalization data has only been available since 2021, but for ILI the data has been available since 2010 and has been successfully forecast for several seasons. % Modeling hospitalization data alone is limited to the relatively small amount of data, 
% but may be supplemented by existing ILI data which has been reported, 
% published at the state level, and successfully forecast for over a decade. 
In this manuscript, we introduce a two component modeling framework for forecasting weekly hospitalizations utilizing both hospitalization data and ILI data. The first component is for modeling ILI data using a dynamic nonlinear Bayesian hierarchical model. The second component is for modeling hospitalizations as a function of ILI. For hospitalization forecasts, ILI is first forecasted and then hospitalizations are forecast with ILI forecasts used as a linear or quadratic predictor. In a simulation study, two ILI forecast models, including one similar to the winning model for two seasons of the CDC forecast competition from \cite{osthus2019dynamic} and a nonlinear Bayesian hierarchical model from \cite{ulloa2019} are compared. Also assessed is the usefulness of including a systematic model discrepancy term in the ILI model. Forecasts of state and national hospitalizations for the 2023-24 flu season are made, and different modeling decisions are compared. We found that including a discrepancy component in the ILI model tends to improve forecasts during certain weeks of the year. We also found that other modeling decisions such as the exact nonlinear function to use in the ILI model or the error distribution for hospitalization models may or may not be better than other decisions, depending on the season, location, or week of the forecast.
% We compare hospitalization forecasts from our model to other related models submitted to the CDC forecasting competition.

@@

\begin{figure}
    \centering
    \includegraphics[scale=.7]{../Images/us_ili_seasons.png}
    \caption{Percentage of outpatient visits with an influenza-like illness (ILI) in the US for seasons 2010 to 2023. Week 1 is the first week of August of the year the flu season begins and the last week of the season is the last week of July of the following year.}
    \label{fig:us_ili}
\end{figure}

@@

 \begin{figure}
    \centering
    \includegraphics[scale=.7]{../Images/ili_vs_week.png}
    \caption{Percentage of outpatient visits with an influenza-like illness (ILI) in five different states and the District of Columbia for seasons 2010 to 2023. Week 1 is the first week of August of the year the flu season begins and the last week of the season is the last week of July of the following year.
     Plots include lines for ILI\% from the 2010 flu season to 2023 (grey) and for the weekly ILI averaged over all seasons (black).}
    \label{fig:ili_vs_week}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.5]{../Images/us_hospitalizations.png}
    \caption{Weekly flu confirmed hospitalization counts at the national level for 2022 (left) and 2023 (right) flu seasons}
    \label{fig:us_hosp}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.65]{../Images/hosp_vs_week.png}
    \caption{Weekly hospitalization counts for five states and DC for the 2022 (grey) and 2023 (black) flu seasons}
    \label{fig:hosp_vs_week}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.6]{../Images/ili_vs_hosp.png}
    \caption{Weekly flu confirmed hospitalization counts ($y$-axis) for five states and the District of Columbia for the 2022 and 2023 flu seasons plotted against ILI\% ($x$-axis)}
    \label{fig:ili_vs_hosp}
\end{figure}

@@

% \begin{figure}
%     \centering
%     \includegraphics[scale=.8]{../Images/hosp_preds_ili_22.png}
%     \caption{Weekly hospitalization counts during the 2022 flu season for 5 states and DC (black dots) and predicted weekly hospitalizations from the fit of model (\ref{eq:simple_hosp_reg}) (red lines)}
%     \label{fig:hosp_preds_ili_22}
% \end{figure}
% \jarad{Make the relationship between the data in the previous plot and this plot clear.}

@@

The proposed model for ILI for any location is given in (\ref{eq:ili_model}). Here $ILI_{s,w}$ is the ILI for flu season $s$ and week $w = 1, 2, ..., W$, where $W = 52$ or $W = 53$, depending on how many Sundays there are in a given season. The ILI is a proportion, so the Beta random variable is a natural selection for modeling. Under the parameterization in of the Beta distribution used in (\ref{eq:ili_model}) the expected value is $\pi_{s,w}$ and the variance is $\pi_{s,w}(1 - \pi_{s,w})/(1 + \kappa_s)$, making $\kappa_s$ a scale parameter. The nonlinear function $f_{\theta_s}(w)$ captures the trajectory of the ILI, and $\gamma_w$ is a discrepancy term for capturing the systematic patterns which $f_{\theta_s}(w)$ does not capture. 
\begin{equation}
\begin{aligned}
    \label{eq:ili_model}
    % \begin{flalign*}
        ILI_{s,w} &\overset{ind}{\sim} \text{Beta}(\pi_{s,w}\kappa_s,\; \kappa_s(1 - \pi_{s,w})) \\
        \text{logit}(\pi_{s,w}) &= f_{\theta_s}(w) + \gamma_w
    % \end{flalign*}
\end{aligned}
\end{equation}
In \cite{osthus2019dynamic} $f_{\theta_s}(w) = \text{logit}(I_{s,w})$ where $I_{s,w}$ is the infectious compartment of the SIR model from (\ref{eq:sir_diff}) in section \ref{sec:sir_func}. In \cite{ulloa2019} $f_{\theta_s}(w) = ASG_{\theta}(w)$ from (\ref{eq:asg_function}) in section \ref{sec:asg_func}. In \cite{ulloa2019} modeling is done hierarchically over seasons. 
% The SIR and ASG functions are defined in the next two subsections.
% and $\gamma_w$ is modeled as a reverse random walk as in (\ref{eq:rw}).

@@

\begin{figure}
    \centering
    \includegraphics[scale=.6]{../Images/sir_traj.png}
    \caption{Susceptible-infectious-recovered (SIR) model separated by compartments. The three compartments are the susceptible compartment (left), infectious (center), and recovered (right). In this example, $S_0/\rho > 1$.}
    \label{fig:sir_traj}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.45]{../Images/asg_function.png}
    \caption{Example plot of asymmetric Gaussian (ASG) function showing the shape of the function in relation to the parameters $\lambda, \; \eta, \; \mu, \; \sigma_1, \; \text{and} \; \sigma_2$}
    \label{fig:asg_function}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.5]{../Images/asg_fits.png}
    \caption{Observed US national influenza-like illness (ILI) percentage for seasons 2010 to 2022 excluding 2020 (grey) overlaid with MLE of an asymmetric Gaussian (ASG) model for the ILI data (black)}
    \label{fig:asg_fits}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.45]{../Images/discrepancy.png}
    \caption{Difference between observed US national influenza-like illness (ILI) and MLE fits for an asymmetric Gaussian (ASG) model for each season 2010 to 2022 excluding 2020 (grey) and the average difference of all seasons (black)}
    \label{fig:discrepancy}
\end{figure}

The term $\gamma_w$, where $w$ is the season week, is included in (\ref{eq:ili_model}) to capture the per week discrepancy between ILI and the function. Modeling discrepancy has been used in uncertainty analysis of simulators to capture systematic differences between mathematical models and 
reality \cite[]{ma2022multifidelity,brynjarsdottir2014learning,arendt2012improving,kennedy2001bayesian}. Modeling discrepancy can lead to overfitting, particularly in forecasting scenarios, and may also lead to identifiability issues. 
Thus, care must be taken in setting parameter constraints as well as in the selection of prior distributions \cite[]{osthus2019dynamic,brynjarsdottir2014learning}. 
Modeling of the discrepancy for ILI was done by \cite{osthus2019dynamic} during the 2015 and 2016 flu seasons where their model outperformed all others in the CDC flu forecasting challenge \cite[]{osthus2019dynamic}. As in Osthus's model, $\gamma_w$ is modeled as a reverse random walk, as shown in (\ref{eq:rw}). 
\begin{equation}
    \label{eq:rw}
        \gamma_w|\gamma_{w + 1} \overset{ind}{\sim} N(\gamma_{t+1},\sigma^2_{\gamma}), \quad
        \gamma_{W} \sim N(0,\sigma^2_{\gamma_W})
\end{equation}
The idea for using the reverse random walk is that there are several previous seasons of ILI data, and assuming the random walk captures systematic behavior, fitting it hierarchically over seasons can assist in predicting future behavior in the current season. 
Reverse random walks have also been used with success in election forecasting and other flu forecasting models \cite[]{osthus2021multiscale, osthus2019dynamic, linzer2013dynamic}. The sum to zero constraint $-\gamma_1 = \sum_{w=2}^W \gamma_w$ is imposed on (\ref{eq:rw}) to improve identifiability.

@@

% \begin{equation}
%     \label{eq:shared_priors}
%     \begin{align*}
%         \kappa_s &\overset{ind}{\sim} N^+(0, 10,000^2) \\
%         \sigma_{\gamma}^2 &\sim N^+(0, .02^2) \\
%         \sigma_{\gamma_W}^2 &\sim N^+(\hat{\sigma}_W^2, 1^2) \\
%         \alpha_{0s} &\overset{ind}{\sim} N(0, 5^2) \\
%         \alpha_{1s} &\overset{ind}{\sim} N(0, 5^2) \\
%         \alpha_{2s} &\overset{ind}{\sim} N(0, 5^2) \\
%         \phi &\sim N(0, .4)\mathbb{1}_{(-1,1)} \\
%         \sigma_{\epsilon_s} &\overset{ind}{\sim} N^+(0, 4^2) \\
%         \omega_s &\overset{ind}{\sim} N^+(0, 15^2)
%     \end{align*}
% \end{equation}
% \jarad{Generally introduce the distribution families in the methods, but the distributions themselves when performing the data analysis. Here I think you just need to say that you are using normals for unrestricted parameters, positive normals for positive parameters and a normal truncated on (-1,1) for the correlation. Also mention they are all independent (which I guess was done before.}

@@

The models were fit via Markov chain Monte Carlo (MCMC) sampling using the \texttt{cmdstanr} package which was developed and is maintained by the \cite{stan2024manual} \cite[]{gabry2022stan}. Stan implements Hamiltonian Monte Carlo (HMC) sampling with the No-U-turn sampler \cite[]{hoffman2014no}. The \texttt{cmdstanr} package provides several diagnostic statistics for assessing the sampler.
As mentioned, most model parameter prior distributions were intended to be uninformative. 
% Figures \ref{fig:posterior_theta_sir} - \ref{fig:hosp_nus_param} in appendix \ref{app:B_prior} shows plots of posterior distributions for select parameters from ILI and hospitalization models.
Plots of posterior distributions for select parameters from ILI and hospitalization models are shown in the supplementary material.

@@

\begin{table}
\caption{Maximum $\hat{R}$ and minimum $ESS$ over all parameters for six hospitalization models fitted on US data for week 14 of the 2023 season}
\label{tab:hsop_diagnostics}
\begin{center}
    \begin{tabular}{c|cccccc}
     & NORM & NORM$^2$ & LNORM & LNORM$^2$ &  LST &  LST$^2$ \\
     \hline
     $\hat{R}$ & $< 1.001$ & $< 1.001$ & $< 1.001$ & $< 1.001$ & $< 1.001$ & $< 1.001$\\
     $ESS$  & 71,266 & 73,554 & 46,747 & 54,975 & 7,660 & 62,663 \\
    \end{tabular}
    \end{center}
\end{table}

@@

\begin{equation}
    \text{CRPS}(F, y^*) = \int_{-\infty}^{\infty} (F(x) - \mathbb{1} (y^* \leq x))^2 dx
    \label{eq:crps2}
\end{equation}

@@

\begin{figure}
\centering
% \begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[scale=.35]{../Images/overall_crps.png}
    % \caption{Boxplots of CRPS for the four ILI models over all seasons, weeks, and horizons in the simulation study}
% \end{subfigure}%
% \begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[scale=.35]{../Images/overall_logs.png}
    % \caption{Boxplots of LogS for the four ILI models over all seasons, weeks, and horizons in the simulation study}}
% \end{subfigure}
\caption{Boxplots of the continuous ranked probability score (CRPS) (left) and logarithmic score (LogS) (right) for the four ILI models over all seasons, weeks, and horizons in the simulation study}
\label{fig:overall_scores}
\end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[scale=.6]{../Images/overall_crps.png}
%     \caption{Boxplots of CRPS for the four ILI models over all seasons, weeks, and horizons in the simulation study}
%     \label{fig:crps_overall}
% \end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.5]{../Images/crps_by_season.png}
    \caption{Boxplots of continuous ranked probability score (CRPS) for the four ILI models over all weeks and horizons in the simulation study faceted by season and including seasons 2010-2022, excluding 2020}
    \label{fig:crps_by_season}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.5]{../Images/crps_by_week_horizon.png}
    \caption{Boxplots of continuous ranked probability score (CRPS) for the four ILI models over all seasons in the simulation study faceted by horizon (x-axis) and week (y-axis). Horizons include 1-4 week ahead forecastss and weeks include weeks 14, 20, 26, 32, and 38 of the flu season}
    \label{fig:crps_by_week_horizon}
\end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[scale=.6]{../Images/overall_logs.png}
%     \caption{Boxplots of LogS for the four ILI models over all seasons, weeks, and horizons in the simulation study}}
%     \label{fig:logs_overall}
% \end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.5]{../Images/logs_by_season.png}
    \caption{Boxplots of logarithmic score (LogS) for the four ILI models over all weeks and horizons in the simulation study faceted by season and including seasons 2010-2022, excluding 2020.}
    \label{fig:logs_by_season}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.5]{../Images/logs_by_week_horizon.png}
    \caption{Boxplots of logarithmic (LogS) for the four ILI models over all seasons in the simulation study faceted by horizon (x-axis) and week (y-axis). Horizons include 1-4 week ahead forecasts and weeks include weeks 14, 20, 26, 32, and 38 of the flu season.}
    \label{fig:logs_by_week_horizon}
\end{figure}

@@

In this section we apply the forecast models to make forecasts of the 2023 flu season weekly hospitalizations. The scoring of the forecasts is in the context of the FluSight competition where each competing forecast was submitted as a set of 23 quantiles corresponding to the given probability levels $(0.010, 0.025, 0.050, 0.100, 0.150, …, 0.950, 0.975, 0.990)$. A single forecast is thus comprised of 11 predictive intervals and a median.
Forecasts of 1, 2, 3, and 4-week ahead hospitalization counts were requested, and forecasts were made at the state and national level. The first week of forecasting took place during the week of October 7, 2023, and the final week was the week of April 27, 2024 making 29 total weeks of forecasts.
 The same format was used during the 2021 and 2022 seasons and for the COVID-19 Forecast Hub \cite[]{mathis2024evaluation, bracher2021evaluating}. 
% Nearly teams participated and forecasts from over 40 models were submitted throughout the duration of the season. 
 Primary scores for evaluating each forecast were the weighted interval score (WIS), the log-weighted interval score (LWIS), and the relative weighted interval score (RWIS). The focus in this section will be on the LWIS (see supplementary material for RWIS based results).

@@

\begin{equation}
\label{eq:is}
        IS_{\alpha}(l,r;y^*) = (r-l) + \frac{2}{\alpha}(l - y^*)\mathbb{1}\{y^* < l\} + \frac{2}{\alpha}(y^* - r) \mathbb{1}\{y^* > r\}
\end{equation}

We fit 24 forecast models for each location for all 29 weeks, and for each week forecast 1-4 week ahead hospitalizations. The 24 models included all combinations of ASG, ASGD, SIR, and SIRD ILI models, the NORM, LNORM, and LST hospitalization models, and both quadratic and linear hospitalization models. 
The prior distributions under the SIR model are in (\ref{eq:sir_prior}). Because we set $S_{0s} = 0.9$, prior distributions were assigned only to $I_{0s}$, $\beta_s$ and $\rho_s$, recalling the parameter for the recovery rate $\delta_s = \rho_s \beta_s$. Here $\mathbb{1}_{A}$ represents the indicator function for values within the set $A$.

\begin{equation}
\begin{aligned}
    \label{eq:sir_prior}
        I_{0s} &\sim N(0.005, 0.03) \mathbb{1}_{(0, .1)} \\
        \beta_s &\sim N^+(0.8, 0.3) \\
        \rho_s &\sim N^+(0.68, 0.08)
\end{aligned}
\end{equation}
For the ASG model, the MLE $\hat{\theta}_s = (\hat{\lambda}_s, \hat{\eta}_s, \hat{\mu}_s, \hat{\sigma}_{1s}^2, \hat{\sigma}_{2s}^2)$ was calculated and $\hat{\lambda}_s$ was accepted as a fixed value. The remaining estimates were used as starting values for posterior sampling. The transformation $T(\theta_s) = (\text{log}(\eta_s), \mu_s, \text{log}(\sigma_{1s}^2), \text{log}(\sigma_{2s}^2))$ was made, and a prior distribution was assigned to $T(\theta_s)$.
The prior distributions for the ILI model under the ASG function are shown in (\ref{eq:ili_prior}). These are slightly informative priors because for most parameters we have an idea what reasonable values may be. Here $m = (0.3, 23, 3.69, 4.7)$ and $C = \text{diag}(0.2, 5, 2, 2)$
where $\text{diag}(\cdot)$ 
is the diagonal matrix for the given entries.
